Supporting information

### 2023-10-31 paper/supporting_information.qmd

For the missing-data dataset XXX.

>>>>

For the missing-data dataset 250 post-warmup samples were taken from 4
indpendent Markov  chains after 100 warmup samples. The sampling was initialised
using the mass matric from the complete measurement dataset and the warmup 
consisted of step size adaption for 100 samples. The resulting posterior distribution
had an $\hat{R} = 1.01$ for the log-probability and did not exhibit post-warmup 
divergences that were not a result of differential equation errors.
